A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-30 paper.tex
Work in progress
References improvement

One of the problems that we have identified in this research is that most
bio-inspired algorithms are designed with a traditionally sequential
perspective \cite{back1996evolutionary} [X-Z], where each process must wait for
the previous task to finish before continuing. Some architectures address this
issue \cite{valdez2021container,garcia2015evospace,merelo2016nodio}, what
distinguishes us, is that our proposal presents an algorithm designed in its
entirety as a native solution in the cloud, fully distributed, where its
processes are executed in parallel and asynchronously. This technique makes it
easy to scale the computing power according to the complexity required by the
problem \cite{armbrust2010view}.

@@

One of the publications with the most influence on our research proposes a
cloud-native optimization framework, that can include multiple
(population-based) algorithms~\cite{valdez2021container}. In their research,
they work with ideas such as those mentioned in Figure~\ref{fig1}.

\begin{figure}
    \centering
    \includegraphics[width=80mm]{img/fig1_background.pdf}
    \caption{These ideas planted the seed of thought in our current presentation.} \label{fig1}
    \end{figure}

>>>>

One of the problems that we have identified in this research is that most
bio-inspired algorithms are designed with a traditionally sequential
perspective \cite{porto2018evolutionary,back1996evolutionary}, where each
process must wait for the previous task to finish before continuing. Some
architectures address this issue
\cite{valdez2021container,garcia2015evospace,merelo2016nodio}, what
distinguishes us, is that our proposal presents an algorithm designed in its
entirety as a native solution in the cloud, fully distributed, where its
processes are executed in parallel and asynchronously. This technique makes it
easy to scale the computing power according to the complexity required by the
problem \cite{armbrust2010view}.

@@

Many of the publications with the most influence on our research
~\cite{valdez2021container,garcia2021event,merelo2016performance,merelo2016nodio}
propose a cloud-native optimization architecture that features population-based
algorithms. They present ideas such as those mentioned in Figure~\ref{fig1},
which planted the seed of thought in our current paper.

\begin{figure}
    \centering
    \includegraphics[width=80mm]{img/fig1_background.pdf}
    \caption{These ideas planted the seed of thought in our algorithm proposal.} \label{fig1}
    \end{figure}
